\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-06-06 response-to-reviewer-comments.tex

\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``The manuscript is well written and the work is of interest to the applied superconductivity community.''

    {\bf Author response:} We are glad that the reviewer found the paper to be well written, and we agree that the software and manuscript will be valuable to the applied superconductivity community.
    }
    \item{
    {\bf Reviewer comment:} ``The software works, although the implementation is a bit slower and more memory hungry than commercial or closed-source tools.''

    {\bf Author response:} It is true that the software favors portability and simplicity of implementation over raw performance, likely making it less efficient than some commercial or closed-source tools. We do not see SuperScreen as a competitor to or replacement for superconducting electronic design automation (EDA) and inductance extraction tools such as InductEx and FastHenry. Rather, we see SuperScreen as a complementary research tool for modeling experiments involving 2D superconductors and mesoscopic superconducting devices, as opposed to designing superconducting integrated circuits. 
    }
    \item{
    {\bf Reviewer comment:} ``The reference to [16] for a review of inductance extraction is a bit old -- newer tools and methods and publications exist.''

    {\bf Author response:} Reference [16] (Gaj, \emph{et al.}) is indeed a bit old. We have added more recent references about inductance extraction tools to Appendix A. In particular, Tolpygo, \emph{et al.} 2021 Supercond. Sci. Technol. {\bf 34} 085005 (which is now cited as reference [20]) and references [8--25] therein provide a thorough and up-to-date survey of inductance extraction software.
    }
    \item{
    {\bf Reviewer comment:} ``P.4, Left Column, Line 53: `though' should be `through'.''

    {\bf Author response:} Thank you for reading the manuscript carefully and catching this typo. The typo has been fixed in the revised version of the manuscript.
    }
\end{itemize}

@@

\section{Reviewer 2}
\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``Highlights and graphical abstract could be provided.''

    {\bf Author response:} Thank you for the suggestion. We have included highlights and a graphical abstract in the revised submission.
    }
    \item{
    {\bf Reviewer comment:} ``As there are many other similar works available, please provide a strong literature survey.''

    {\bf Author response:} The introductory section provides a survey of the literature of numerical modeling of 2D superconductors (references 1--20). In terms of surveying available software tools, we have added more recent references about inductance extraction tools to Appendix A. In particular, Tolpygo, \emph{et al.} 2021 Supercond. Sci. Technol. {\bf 34} 085005 (which is now cited as reference [20]) and references [8--25] therein provide a thorough and up-to-date survey of inductance extraction software.
    }
    \item{
    {\bf Reviewer comment:} ``A comparison of the work with state of the art is necessary.''

    {\bf Author response:} Figure 4 provides a comparison between SuperScreen, 3D-MLSI, LCR2D, and the axisymmetric model by  Brandt and Clem. The problem shown in Figure 4 (the self-inductance of an annulus as a function of the effective penetration depth $\Lambda$, inner radius $a$, and outer radius $b$) is the only problem for which we were able to find solutions from multiple methods in the literature. This problem also has an analytical solution in the limit $\Lambda=0$ and $a/b\to 0$. All of the numerical methods, including SuperScreen, agree well with the analytical solution in this limit.

    To the best of our knowledge, the ``state of the art'' commercial tool for modeling the magnetic response of superconductors is InductEx. We have added to Appendix A an example problem from the InductEx user manual, namely the self-inductance of a thin film square washer. Code Block 3 in Appendix A, which we have added in the revised version of the manuscript, demonstrates that SuperScreen and InductEx agree to within 1\% on this problem.
    }
\end{itemize}

\section{Inhomogeneous films}

After submitting the manuscript and posting the submitted version to arXiv.org, Dr. Vladimir G. Kogan brought to our attention his work on London modeling of superconductors with inhomogeneous penetration depth (V. G. Kogan \& J. R. Kirtley, Phys. Rev. B {\bf 83}, 214521 (2011)) and pointed out the existence of an additional term in the 2nd London equation for inhomogeneous superconductors, which is proportional to the gradient of the effective penetration depth, $\vec{\nabla}\Lambda$.

We have modified the software so that this term is included if the user specifies an inhomogeneous penetration depth and have moved all discussion of inhomogeneous films from the main text into Appendix C, where we have clarified the applicability of the London model to films with inhomogeneous penetration depth based on V. G. Kogan \& J. R. Kirtley, Phys. Rev. B {\bf 83}, 214521 (2011) and J. R. Cave \& J. E. Evetts, Journal of Low Temperature Physics {\bf 63}, 35–55 (1986) (references [52] and [51] respectively in the revised manuscript). We also removed from Appendix C the example code (Code Block 3: Simulating an inhomogeneous superconducting device) and the accompanying Figure C.7. The main results of the manuscript are completely unchanged.
\end{document}

### 2022-06-06 main.tex

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.25
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_points=3500, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
# Visualize the solution.
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
\label{code:device}
\end{code}

@@

Here, we briefly describe existing software tools for modeling the magnetic response of superconducting devices, most of which are specifically designed for inductance extraction for superconducting integrated circuits. FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}. This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system. FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}. A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source. For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}. For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.

\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools. One such problem, provided as an example in the InductEx user manual, is the self-inductance $L$ of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$, for which the InductEx solution reports a ``design'' value of $L=20\,\mathrm{pH}$ and an ``extracted'' value of $L=20.0956\,\mathrm{pH}$~\cite{inductex_user_manual_2020}. Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen. The inductance extracted using \SuperScreen is within 1\% of the inductance extracted using InductEx.

@@

layer = sc.Layer(
    "base",
    london_lambda=0.24,
    thickness=0.2,
)
film = sc.Polygon(
    "washer",
    layer="base",
    points=box(30, points_per_side=50),
)
hole = sc.Polygon(
    "hole",
    layer="base",
    points=box(10, points_per_side=250),
)
device = sc.Device(
    "washer",
    layers=[layer],
    films=[film],
    holes=[hole],
    length_units="um",
)
device.make_mesh(min_points=3000)
# See Equation 19.
M = device.mutual_inductance_matrix()
L = M[0, 0].to("pH")
print(f"Inductance = {L:~.4fP}")
# Output: Inductance = 19.9100 pH
\end{minted}
\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer. The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}. }
\label{code:washer}
\end{code-onecol}

>>>>

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.25
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_points=3500)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
# Visualize the solution.
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
\label{code:device}
\end{code}

@@

Here, we briefly describe existing software tools for modeling the magnetic response of superconducting devices, most of which are specifically designed for inductance extraction for superconducting integrated circuits. FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}. This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system. FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}. A 2D London-Maxwell approach based on a scalar stream function, much like the approach used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source. For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}. For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.

\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools. One such problem, provided as an example in the InductEx user manual, is the self-inductance $L$ of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$, for which the InductEx solution reports a ``design'' value of $L=20\,\mathrm{pH}$ and an ``extracted'' value of $L=20.0956\,\mathrm{pH}$~\cite{inductex_user_manual_2020}. Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen. The inductance extracted using \SuperScreen, $L=19.91\,\mathrm{pH}$, is within 1\% of the inductance extracted using InductEx.

@@

layer = sc.Layer(
    "base",
    london_lambda=0.24,
    thickness=0.2,
)
film = sc.Polygon(
    "washer",
    layer="base",
    points=box(30, points_per_side=50),
)
hole = sc.Polygon(
    "hole",
    layer="base",
    points=box(10, points_per_side=250),
)
device = sc.Device(
    "washer",
    layers=[layer],
    films=[film],
    holes=[hole],
    length_units="um",
)
device.make_mesh(min_points=3000)
# See Equation 19.
M = device.mutual_inductance_matrix()
L = M[0, 0].to("pH")
print(f"Inductance = {L:~.4fP}")
# Output: Inductance = 19.9100 pH
\end{minted}
\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$. The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}. }
\label{code:washer}
\end{code-onecol}
